Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2023-02-10 src/tex/ms.tex
Add KDE sentence

We apply the method described in section \textbf{\ref{subsec:stats}} to the first GW event GW150914 \citep{GW150914}.
We use the \texttt{Overall\_posterior} posterior samples for GW150914,
publicly available from the Gravitational wave Open Science Center \citep{LIGOScientific:2019lzm}. 
The parameters involved in the analysis and the range we allow for the inference are tabulated in table \ref{tab:parameters}.
The spin of BHs formed in isolated binaries depends strongly on the angular
momentum transport in massive stars which is still highly uncertain (see however \citet{Fuller2019, Bavera2020}),
therefore we only consider the two component masses in the observable space $\bm{\theta}$ in both the
root-finding stage and the MCMC stage.

@@

For hyperparameters $\bm{\lambda}$, we choose parameters that strongly affect
binary evolution in \texttt{COSMIC} for massive stars, including the common envelope
efficiency $\alpha$, the fraction of mass accreted onto the accretor during stable mass transfer $f_{\rm acc}$,
the critical mass ratio which determines whether Roche-overflow mass transfer
proceeds stably or produces a common envelope when the donor star is on the Hertzsprung gap
$q_{\rm crit,3}$, and the root-mean-square of the Maxwellian distribution
employed for CO natal kicks, $\sigma$. 
%Prior

>>>>

We apply the method described in section \textbf{\ref{subsec:stats}} to the
first GW event GW150914 \citep{GW150914}. We use the \texttt{Overall\_posterior}
posterior samples for GW150914, publicly available from the Gravitational wave
Open Science Center \citep{LIGOScientific:2019lzm}. The parameters involved in
the analysis and the range we allow for the inference are tabulated in table
\ref{tab:parameters}. The spin of BHs formed in isolated binaries depends
strongly on the angular momentum transport in massive stars which is still
highly uncertain (see however \citet{Fuller2019, Bavera2020}), therefore we only
consider the two component masses in the observable space $\bm{\theta}$ in both
the root-finding stage and the MCMC stage. \textbf{Instead of the sampling the posterior
in the two component masses space, we choose to perform the KDE in the chirp
mass and mass ratio space, which are less degenerate and is less prone to error
from the KDE.}

@@

For hyperparameters $\bm{\lambda}$, we choose parameters that strongly affect
binary evolution in \texttt{COSMIC} for massive stars, including the common envelope
efficiency $\alpha$, the fraction of mass accreted onto the accretor during stable mass transfer $f_{\rm acc}$,
the critical mass ratio which determines whether Roche-overflow mass transfer
proceeds stably or produces a common envelope when the donor star is on the Hertzsprung gap
$q_{\rm crit,3}$, and the root-mean-square of the Maxwellian distribution
employed for CO natal kicks, $\sigma$.
